### 2024-03-04 ms.qmd
Updates

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using in R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors. We included a random intercept and slope (trial) for each lizard in our models. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (pmcmc) using the posterior distributions. We considered statistical significance if p~mcmc~  < 0.05.

@@

```{r, resultsRev}
# Rename some of the posteriors and make new estimates for the learning rate for the Reversal task doing the same thing we did in the chunk above.
## 1) L. delicata
deli_CORTCold <- deli$b_trial_reversal
deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold <- guich$b_trial_reversal
guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
```

>>>>

#### Statistical analyses  
We performed the analyses for each species separately. We fitted two different Bayesian multilevel models using the brm function from the _brms_ package [@burkner2017brms] using in R extension (version 2.8.2) [@R]. We ran four parallel MCMC chains of 3000 iterations for each model, with a warmup period of 1000 iterations. We modelled correct choices [correct (1) or not (0)] as the response variable, and trial, hormone (CORT versus Control), incubation temperature (Cold versus Hot), and their interaction as fixed factors. We included a random intercept and slope (trial) for each lizard in our models. We used the posterior distributions of parameters from these models to test for differences in learning rate between treatments and species. Learning slopes were obtained using the ‘trial’ estimates and its interaction with hormone and temperature treatments. Slope estimates greater than zero were considered as evidence of learning, while those less or equal to zero were not. We calculated the probability that slopes or contrasts between slopes differed from zero (p~mcmc~) using the posterior distributions. We considered statistical significance if p~mcmc~  < 0.05.

@@

```{r, results}
#| label: results
# Rename some of the posteriors and make means and sd for the posteriors.
## 1) L. delicata
deli_CORTCold <- deli$b_trial_reversal
deli_ControlCold <- (deli$'b_trial_reversal:cortControl' + deli$b_trial_reversal)
deli_CORTHot <- (deli$'b_trial_reversal:tempHot' + deli$b_trial_reversal)
deli_ControlHot <- (deli$'b_trial_reversal:cortControl:tempHot' + deli$b_trial_reversal + deli$'b_trial_reversal:cortControl' + deli$'b_trial_reversal:tempHot')
## 2) L. guichenoti
guich_CORTCold <- guich$b_trial_reversal
guich_ControlCold <- (guich$'b_trial_reversal:cortControl' + guich$b_trial_reversal)
guich_CORTHot <- (guich$'b_trial_reversal:tempHot' + guich$b_trial_reversal)
guich_ControlHot <- (guich$'b_trial_reversal:cortControl:tempHot' + guich$b_trial_reversal + guich$'b_trial_reversal:cortControl' + guich$'b_trial_reversal:tempHot')
```

```{r, coeficients}
#| label: coeficients
# Getting the Cohen's d coeficients of the (below) between treatments and species comparisons using the formula: 
# d =(mean1 - mean2) / sqrt((sd1^2 + sd2^2)/2)
# For the estimations of the confidence intervals we used Cohen's standard error based on the formula: se = 1 / sqrt(n1-3 + n2-3)
# And critical value:
critical_value <- qnorm((1 + 0.95) / 2)
## A) L. delicata
#### A.1.- CORT
mean_deliControl <- mean(c(deli_ControlCold, deli_ControlHot))
sd_deliControl <- sd(c(deli_ControlCold, deli_ControlHot))
mean_deliCORT <- mean(c(deli_CORTCold, deli_CORTHot))
sd_deliCORT <- sd(c(deli_CORTCold, deli_CORTHot))
#
deli_CORTd <- format_dec((mean_deliControl - mean_deliCORT) / sqrt((sd_deliControl^2 + sd_deliCORT^2)/2), 3)
#
standard_error <- 1 / sqrt((n_list$delicata_Control_Cold + n_list$delicata_Control_Hot)- 3 + (n_list$delicata_CORT_Cold + n_list$delicata_CORT_Hot) - 3)

#
#### A.2.- Temperature
mean_deliCold <- mean(c(deli_ControlCold, deli_CORTCold))
sd_deliCold <- sd(c(deli_ControlCold, deli_CORTCold))
mean_deliHot <- mean(c(deli_CORTHot, deli_ControlHot))
sd_deliHot <- sd(c(deli_CORTHot, deli_ControlHot))
#
deli_Tempd <- format_dec((mean_deliHot - mean_deliCold) / sqrt((sd_deliHot^2 + sd_deliCold^2)/2), 3)
#
#### A.3.- Interaction

#
## B) L. guichenoti
#### B.1.- CORT
mean_guichControl <- mean(c(guich_ControlCold, guich_ControlHot))
sd_guichControl <- sd(c(guich_ControlCold, guich_ControlHot))
mean_guichCORT <- mean(c(guich_CORTCold, guich_CORTHot))
sd_guichCORT <- sd(c(guich_CORTCold, guich_CORTHot))
#
guich_CORTd <- format_dec((mean_guichControl - mean_guichCORT) / sqrt((sd_guichControl^2 + sd_guichCORT^2)/2), 3)
#
#### B.2.- Temperature
mean_guichCold <- mean(c(guich_ControlCold, guich_CORTCold))
sd_guichCold <- sd(c(guich_ControlCold, guich_CORTCold))
mean_guichHot <- mean(c(guich_CORTHot, guich_ControlHot))
sd_guichHot <- sd(c(guich_CORTHot, guich_ControlHot))
#
guich_Tempd <- format_dec((mean_guichHot - mean_guichCold) / sqrt((sd_guichHot^2 + sd_guichCold^2)/2), 3)
#
#### B.3.- Interaction
